Bayesian phylogenetic estimation of fossil ages reveals remarkable consistency of rocks and clocks

### 2015-08-17 fossilDating.tex
hominins

In this paper we have demonstrated that even a small number of morphological characters (some of the fossils had as few as 7 morphological traits coded) can be used in the context of a rich fossil reference data set, to provide an accurate and precise age of the fossil based on a phylogenetic model. The median error in age estimates for the penguin data set we analysed here was 2 My, using either a very simple or a more complex model of morphological change. In both cases we used the new fossilized birth-death tree prior, which is a crucial ingredient in allowing for the estimating of fossil ages under a birth-death tree prior.

>>>>

In this paper we have demonstrated that even a small number of morphological characters (some of the fossils had as few as 7 morphological traits coded) can be used in the context of a rich fossil reference data set, to provide an accurate and precise age of the fossil based on a phylogenetic model. The median error in age estimates for the penguin data set we analysed here was 2 My, using either a very simple or a more complex model of discrete morphological change. In both cases we used the new fossilized birth-death tree prior, which is a crucial ingredient in allowing for the estimating of fossil ages under a birth-death tree prior.
